The College Application Problem

### 2022-05-03 slides_20min/slides.tex
split slides into 8- and 20-minute versions; translations

\begin{frame}{Existing solutions}

In practice, most use \textbf{distributive heuristics} such as distributing applications evenly among attractive, selective ``reach schools'' and less-attractive ``safety schools.'' Turns out to be a \textbf{risk-averse} approach.

@@

Our algorithms provide both \textbf{time and accuracy guarantees}.

@@

\begin{frame}{Algorithms for the general problem}
The general problem is \textbf{NP-complete} (reduction from knapsack). We offer four algorithms:
\begin{itemize}
\item A linear relaxation and \textbf{branch-and-bound scheme}. Primarily of theoretical interest.

@@

Existence of FPTAS suggests college application is \textbf{a relatively easy instance of submodular maximization} (cf. Kulik et al. 2013).
\end{frame}

@@

\begin{frame}{Conclusion}
``Maximax form,'' integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, memory-usage improvements.
\end{frame}

\begin{frame}[allowframebreaks]{\ifen References \else 참고 문헌 \fi}
\scriptsize
\parskip 0em
\leftskip 2em
\parindent -2em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.

>>>>

\ifen {
\begin{frame}{Existing solutions}
In practice, most use \textbf{distributive heuristics} such as distributing applications evenly among reach, target, and safety schools. Turns out to be a \textbf{risk-averse} approach.

@@

Our algorithms provide both \textbf{time and accuracy guarantees}. 
\end{frame}
} \else {
\begin{frame}{기존의 해법}
입학 컨설팅 산업에서는 주로 ``상향·소신·안정 지원 학교'' 각각 균일하게 지원하는 \textbf{배분적 휴리스틱}을 사용하며, \textbf{위험 회피적인} 전략임을 알 수 있다.

또한 \textbf{선형화 휴리스틱}이 있다. $c_j$에만 지원할 때 기대 효용이 $f_j t_j$이므로 다음 배낭 문제를 대리 문제로 푼다.
\[\text{maximize}~~\sum_{j\in \mathcal{X}} f_j t_j \qquad \text{subject to}~~\sum_{j\in \mathcal{X}}g_j \leq H \]
이의 \textbf{근사 계수가 $\mathbf{0}$에 무한히 가까운} 예시를 만들 수 있다.

Fu (2014)는 비슷한 문제를 \textbf{열거법}으로 풀었으며, $m \geq 20$일 때 불현실적인 방법이다.

본 연구가 제시하는 알고리즘은 \textbf{계산 시간과 정확도를 보장한다}. 
\end{frame}
} \fi

@@

\ifen {
\begin{frame}{Algorithms for the general problem}
The general problem is \textbf{NP-complete} (reduction from knapsack). We offer four algorithms:
\begin{itemize}
\item A linear relaxation and \textbf{branch-and-bound scheme}. Primarily of theoretical interest.

@@

Existence of FPTAS suggests college application is \textbf{a relatively easy instance of submodular maximization} (cf. Kulik et al. 2013).
\end{frame}
} \else {
\begin{frame}{일반 문제를 위한 알고리즘}
일반적인 문제는 \textbf{NP-complete} (배낭 문제에서 변환). 4개의 알고리즘 제시:
\begin{itemize}
\item 선형 완화 문제와 해당 \textbf{branch-and-bound} 해법. 주로 이론적인 흥미가 있다.

\item \textbf{지원 지출액 기반 동적 계획}. (의사 다항) $O(Hm + m\log m)$ 시간에 정확한 해를 구하며, $g_j$가 작은 정수가 되는 ``전형적'' 인스턴스에 대해 매우 효율적인 해법.

\item 포트폴리오 가치의 라운딩을 이용한 다른 동적 계획. $O(m^3 / \varepsilon)$ 시간에 $(1 - \varepsilon)$-근사해를 출력하므로 \textbf{FPTAS}!
\item \textbf{Simulated annealing} 휴리스틱. 빠르고 거의 항상 최적의 2\% 이내에 해를 구한다.
\end{itemize}

FPTAS의 존재성은 대학 지원 문제가 \textbf{submodular 최대화의 비교적 쉬운 인스턴스}임을 의미한다 (cf. Kulik et al. 2013).
\end{frame}
} \fi

@@

\ifen {
\begin{frame}{Conclusion}
``Maximax'' form, integrality constraints make the college application problem \textbf{theoretically interesting}. Formally, it is a submodular maximization problem, but its approximability is more like knapsack.

@@

Lots of extensions to consider: parametric risk aversion, distribution constraints, memory-usage improvements.
\end{frame}
} \else {
\begin{frame}{Conclusion}
``Maximax'' 형태와 정수 조건 때문에 대학 지원 문제에는 \textbf{이론적으로 흥미}가 있다. Submodular 최대화 문제이지만, 근사 해법 성질은 배낭 문제에 더 가깝다.

$g_j=1$의 특수한 경우의 포함 사슬 관계 성질도 배낭 문제와 유사하며, 증명 과정은 좀 더 미묘하다.

좋은 대학 지원 전략에는 \textbf{금전적 가치}가 있다. 미국 입학 컨설컨트의 시간당 급료는 평균 200달러! ⇒ 공공 이익을 위해 코드는 open source license로 공개.

문제를 확장할 수 있는 향후 연구: 위험 회피 모수, 배분적 (가나다군) 제약 조건, 메모리 소모량 절감.
\end{frame}
} \fi

\begin{frame}{\ifen References \else 참고 문헌 \fi}
\small
\parskip 0em
\leftskip 1.5em
\parindent -1.5em
%Balas, Egon and Eitan Zemel. 1980. ``An Algorithm for Large Zero-One Knapsack Problems.'' \emph{Operations Research} 28 (5): 1130--54. \url{https://doi.org/10.1287/opre.28.5.1130}.
